---
title: "**Nanodrop Experiment**"
author: "Paslay"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
    collapse: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(plotly)
library(tidyverse)
```

## **About**

- This information is related to absorbance and wavelength values for different treatment groups.

# **All measurements (static plots)**

```{r}
dat <- read.csv("nanodrop_experiment.csv", header = TRUE)

colnames(dat)[2] <- "Treatment" # changing the column name
```

## Selecting by group using ggplot (TRNA)

```{r}
a <- dat %>% 
  filter(type == "TRNA") %>% 
  ggplot(aes(x = wavelength, y = absorbance, color = Treatment))+ 
  geom_point(size = 3, alpha = .5)+
  geom_smooth(size = 1, se = FALSE, method = "loess", 
              fullrange = FALSE, level = 0.95, span = 0.4, linetype = 1)+
  scale_color_brewer(palette = "Set2")+
  theme_classic()+
  labs(title = "Nanodrop of TRNA",
        x = "Wavelength (nm)",
        y = "Absorbance")+
  theme(legend.position = "top")
a
```

## Selecting by group using ggplot (TDNA)

```{r}
a <- dat %>% 
  filter(type == "TDNA") %>% 
  ggplot(aes(x = wavelength, y = absorbance, color = Treatment))+ 
  geom_point(size = 3, alpha = .5)+
  geom_smooth(size = 1, se = FALSE, method = "loess", 
              fullrange = FALSE, level = 0.95, span = 0.4, linetype = 1)+
  scale_color_brewer(palette = "Set2")+
  theme_classic()+
  labs(title = "Nanodrop of TDNA",
        x = "Wavelength (nm)",
        y = "Absorbance")+
  theme(legend.position = "top")
a
```

## Selecting by group using ggplot (Protein)

```{r}
a <- dat %>% 
  filter(type == "Protein") %>% 
  ggplot(aes(x = wavelength, y = absorbance, color = Treatment))+ 
  geom_point(size = 3, alpha = .5)+
  geom_smooth(size = 1, se = FALSE, method = "loess", 
              fullrange = FALSE, level = 0.95, span = 0.4, linetype = 1)+
  scale_color_brewer(palette = "Set2")+
  theme_classic()+
  labs(title = "Nanodrop of Protein",
        x = "Wavelength (nm)",
        y = "Absorbance")+
  theme(legend.position = "top")
a
```

```{r, include=FALSE}
# This is a very cool tool!
ggplotly(a)
```

# **Interactive plots**

## Creating a plot for the Total RNA (plotly)

```{r}
fig <- dat %>%
  filter(type == "TRNA") %>% 
  plot_ly(x = ~wavelength, y = ~absorbance, color = ~Treatment) %>%
  add_lines(line = list(shape = "spline", smoothing = 1.3)) %>% 
  add_trace(type = "scatter", showlegend = FALSE)
fig
#plotly_IMAGE(fig, format = "png", out_file = "output.png")

# I can save the plot if I paste this code into a script
```

## Creating a plot for the Total DNA (plotly)

```{r}
fig <- dat %>%
  filter(type == "TDNA") %>% 
  plot_ly(x = ~wavelength, y = ~absorbance, color = ~Treatment) %>%
  add_lines(line = list(shape = "spline", smoothing = 1.3)) %>% 
  add_trace(type = "scatter", showlegend = FALSE)
fig
#plotly_IMAGE(fig, format = "png", out_file = "output.png")

# I can save the plot if I paste this code into a script
```

## Creating a plot for the Protein (plotly)

```{r}
fig <- dat %>%
  filter(type == "Protein") %>% 
  plot_ly(x = ~wavelength, y = ~absorbance, color = ~Treatment) %>%
  add_lines(line = list(shape = "spline", smoothing = 1.3)) %>% 
  add_trace(type = "scatter", showlegend = FALSE)
fig
#plotly_IMAGE(fig, format = "png", out_file = "output.png")

# I can save the plot if I paste this code into a script
```

# **TRNA, TDNA, Protein seperately (static plots)**

## Creating a plot for the Total RNA alone (ggplot)

```{r}
a <- dat %>% 
  filter(type == "TRNA") %>% 
  filter(Treatment == "TRNA") %>% 
  ggplot(aes(x = wavelength, y = absorbance, color = Treatment))+ 
  geom_point(size = 3, alpha = .5)+
  geom_smooth(size = 1, se = FALSE, method = "loess", 
              fullrange = FALSE, level = 0.95, span = 0.4, linetype = 3)+
  scale_color_brewer(palette = "Set2")+
  theme_classic()+
  labs(title = "Nanodrop of TRNA",
        x = "Wavelength (nm)",
        y = "Absorbance")+
  theme(legend.position = "top")
a
```

## Creating a plot for the Total DNA alone (ggplot)

```{r}
a <- dat %>% 
  filter(type == "TDNA") %>% 
  filter(Treatment == "TDNA") %>% 
  ggplot(aes(x = wavelength, y = absorbance, color = Treatment))+ 
  geom_point(size = 3, alpha = .5)+
  geom_smooth(size = 1, se = FALSE, method = "loess", 
              fullrange = FALSE, level = 0.95, span = 0.4, linetype = 3)+
  scale_color_brewer(palette = "Set2")+
  theme_classic()+
  labs(title = "Nanodrop of TDNA",
        x = "Wavelength (nm)",
        y = "Absorbance")+
  theme(legend.position = "top")
a
```

## Creating a plot for the Protein alone (ggplot)

```{r}
a <- dat %>% 
  filter(type == "Protein") %>% 
  filter(Treatment == "Protein") %>% 
  ggplot(aes(x = wavelength, y = absorbance, color = Treatment))+
  geom_point(size = 3, alpha = .5)+
  geom_smooth(se = FALSE, linetype = 3, span = 0.4)+
  scale_color_brewer(palette = "Set2")+
  theme_classic()+
  labs(title = "Nanodrop of TDNA",
        x = "Wavelength (nm)",
        y = "Absorbance")+
  theme(legend.position = "top")
a
```

